Particle Interception as a Function of Reynolds Number and Collector Density

### 2021-03-07 code/analysis.Rmd
updated after revisions

@@

ANOVA:

@@

residmod <- aov(data = resids, formula = resid ~ loc * ht)

@@

@@

TKEplot <- final %>%
  filter(eta>0) %>%
  arrange(frontal_area, u) %>%
  select(dowel_density, u, eta, deta) %>%
  mutate(TKE = c(1.23, 5.26, 12.2, 9.13, 35.9, 59.6, 11.1, 29.8, 54.4)) %>%
  ggplot(aes(x = TKE, y = eta, ymax = eta + deta, ymin = eta - deta)) +
  geom_point() +
  geom_errorbar() +
  theme_bw() +
  scale_y_continuous(labels = scales::percent) +
  labs(y = "Effective Capture Efficiency", x = expression(paste("Turbulence Kinetic Energy (",mm^{2}/s^{2},")")))

>>>>

#raw data plot

plotstats <- bind_rows(lapply(r2mod,coef)) %>%
  bind_cols(date = as.numeric(names(r2mod)), r2 = unlist(r2val)) %>%
  left_join(metadata) %>%
  rename(int = "(Intercept)", k = t)

rawdataplot <- pumpfinal %>%
  left_join(plotstats) %>%
  mutate(pump_freq = factor(pump_freq, labels = c("Re[c] == 66", "Re[c] == 133", "Re[c] == 200")),
         dowel_density = factor(dowel_density, labels = c("phi[c]==0~'%'", "phi[c] == 0.22~'%'","phi[c] == 0.64~'%'","phi[c] == 1.17~'%'")),
         pred = exp(int + k * t)) %>%
  ggplot(aes(x = t/60, y = mvc, label = round(r2,3))) +
  geom_point() +
  scale_y_log10(breaks = c(10,30,50)) +
  scale_x_continuous(breaks = seq(0,100,by = 20)) +
  facet_grid(pump_freq~dowel_density, labeller = label_parsed) +
  theme_bw() +
  theme(strip.text.y.right = element_text(angle = 0)) +
  geom_line(aes(y = pred), color = "red") +
  geom_text(aes(x = 40, y = 10), alpha = .02, size = 3.5) +
  geom_text(aes(x = 16, y = 10.5, label = "R^2"), parse = TRUE, alpha = .02, size = 3.5) +
  geom_text(aes(x = 25, y = 10, label = "="), alpha = .02, size = 3.5) +
  labs(y = "Measured Concentration (ppm)", x = "Time (minutes)")

ggsave("../pics/rawdata.png", rawdataplot, dpi = 600, height = 5)

@@

ANOVA and conc. profile:

@@

residmod <- aov(data = resids, formula = resid ~ ht)

@@

library(ggridges)

profdata <- pumpfinal %>%
  filter(as.numeric(dowel_density)>0) %>%
  select(date, t, ht, mvc) %>%
  group_by(date, t) %>%
  mutate(prop = mvc/mean(mvc))

profmeans <- profdata %>%
  group_by(ht) %>%
  summarise(mean = round(mean(prop),6), n = n())

profplot <- profdata %>%
  ggplot(aes(x = prop, y = ht, group = factor(ht), fill = factor(ht))) +
  geom_density_ridges(alpha = .7, scale = 1.5) +
  theme_bw() +
  xlim(.75,1.25) +
  geom_vline(xintercept = 1, lty = 3) +
  geom_segment(data = profmeans, aes(x= mean, y = ht, xend = mean, yend = ht + 15, color = factor(ht)), inherit.aes = FALSE, lty = 2, size = .6, alpha = .7) +
  geom_point(data = profmeans, aes(x = mean, y = ht)) +
  scale_color_hue(l = 30) +
  geom_text(data = profmeans, aes(x = .81, y = ht-2, label = paste0("z=",ht,",       ",mean))) +
  geom_text(data = profmeans, aes(x = .792, y = ht-2, label = "bar(x)"), parse = TRUE) +
  geom_text(data = profmeans, aes(x = .8025, y = ht-2, label = "=")) +
  geom_text(data = profmeans, aes(x = .888- c(.003,0,0), y = ht-2, label = paste0(", n=",n))) +
  scale_y_continuous(breaks = c(0,5,14,27,40), minor_breaks = NULL, limits = c(0,45)) +
  theme(legend.position = "none") +
  labs(x = "Normalized Concentration Measurement", y = "Height (cm)", fill = "Height (cm)") +
  coord_cartesian(clip = "off")

ggsave("../pics/profplot.png",profplot,dpi = 600, height = 3, width = 7)

@@

TKEplot <- final %>%
  filter(eta>0) %>%
  arrange(frontal_area, u) %>%
  select(dowel_density, u, eta, deta) %>%
  mutate(TKE = c(1.23, 5.26, 12.2, 9.13, 35.9, 59.6, 11.1, 29.8, 54.4)) %>%
  ggplot(aes(x = TKE, y = eta, ymax = eta + deta, ymin = eta - deta)) +
  geom_point() +
  geom_errorbar() +
  theme_bw() +
  scale_y_log10(labels = scales::percent) +
  labs(y = "Effective Capture Efficiency", x = expression(paste("Turbulence Kinetic Energy (",mm^{2}/s^{2},")")))
